Design and Implementation of Mobile Proxy\\ Case Study: Mobile Data Collection

### 2016-09-05 Paper/23215131-Aris Prawisudatama-Paper Thesis-3rd Rev/Paper.tex
Initial final paper

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

@@

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

@@

@@

\subsection{OSGi Framework}
Ada beberapa implementasi dari OSGi, atau biasa disebut dengan OSGi Framework, antara lain: Apache Felix, Concierge, Eclipse Equinox, JBoss, Hitachi, Knopflerfish, dan ProSyst. Penelitian ini menggunakan Knopflerfish OSGi Framework, karena Knopflerfish telah mengimplementasikan spesifikasi terbaru dari OSGi, yaitu OSGi R6. Selain itu, Knopflerfish juga terbukti dapat diimplementasikan pada Android OS.

@@

\subsubsection{Proxy Server}
Proxy server merupakan sebuah OSGi bundle yang mengimplementasikan embedded web server. Web server yang digunakan dalam penelitian ini adalah Jetty 9 yang merupakan versi tertinggi pada saat ini. Pada Proxy Server Bundle ter-register sebuah service (API) ContextHandlerService yang berfungsi untuk meregister ServletContext yang diinisiasi pada Application Bundle.

\subsubsection{Composite Application}
Composite Application merupakan sebuah OSGi bundle yang mengimplementasikan Web services dan client dalam sebuah bundle. Web services diimplementasikan dalam bentuk Servlets yang terkumpul dalam sebuah context. Sementara client diimplementasikan dalam bentuk web-based application, yang ditulis dengan HTML, Javascript, dan CSS. Selain itu, Composite Application juga menyediakan API yang dapat diimport secara dynamic oleh bundle yang lain, antara lain : AccountHandlerService, DaoHandlerService, dan PropertyHandlerService.

\subsubsection{Synchronizer}
Synchronizer merupakan sebuah OSGi bundle yang digunakan untuk melakukan sinkronisasi data secara dua arah: Remote to Local dan Local to Remote. Synchronizer bundle memerlukan beberapa service yang disediakan oleh Composite Application, antara lain: AccountHandlerService untuk mengakses session yang akan disinkronisasi serta DaoHandlerService untuk mengakses local storage.

\subsection{Android Application}
Secara default, Knopflerfish telah menyediakan implementasi dari OSGi Framework yang dapat dijalankan pada semua sistem operasi yang mendukung Java SE. Tetapi, dikarenakan Android OS menggunakan implementasi JVM yang berbeda, yaitu Dalvik VM, maka perlu dibuat implementasi Knopflerfish yang dapat berjalan di Android OS. Implementasi dibuat

@@

\section{Conclusion and Future Work}
We proposed a mobile proxy design that allows the distribution web service dynamically as a bundle. It is intended to be suitable for current SOA-related standards technologies. It provides transparent resources (i.e. data and web service logics) access using combination of synchronization, replication, and routing mechanisms. Data integration is performed automatically, thus data can be viewed as a unity and does not need to be manually checked to ensure its integrity.

Our proposed design presented in this paper is preliminary result of our research. Our proposed design needs further research, especially in replication mechanism in mobile device, especially android environment, followed by realization for evaluation purpose. Well-designed mechanism will result easy configuration, increase availability, and improve system performance.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

>>>>

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

@@

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

@@

\usepackage{minted}
\usepackage{tcolorbox}
\usepackage{etoolbox}
\BeforeBeginEnvironment{minted}{\begin{tcolorbox}}%
\AfterEndEnvironment{minted}{\end{tcolorbox}}%
\AtBeginEnvironment{minted}{\fontsize{8}{8}}

@@

\subsection{OSGi Framework}
There are several implementations of OSGi, or commonly referred to OSGi Framework, ie: Apache Felix, Concierge, Equinox Eclipse, JBoss, Hitachi, Knopflerfish, and ProSyst. This study uses the Knopflerfish OSGi Framework, because Knopflerfish OSGi Framework has implemented the latest OSGi specification, the OSGi R6. In addition, the Knopflerfish OSGi Framework is also proven to be implemented in Android application.

\subsection{Android Application} \label{ssec:android-application}
By default, Knopflerfish provides an implementation of the OSGi Framework that can be run on any operating system that supports Java SE. However, because the Android OS uses a different JVM implementations, the Dalvik VM, so it needs to be made Knopflerfish OSGi Framework implementations that can run on the Android OS.

Android application that is made must support the principle of OSGi, which is modular. The case studies used in this study is a case study for field data collection, so that the user interface is a questionnaire form. To accelerate the creation and simplify the loading of the page, so it is used Cordova. Cordova is a webview-based, so the control used is an HTML form element. \figurename{\ref{fig:android-app}} shows screenshots of Android application.

\begin{figure}
	\centering
	\subfloat[Home Page]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-1}
		\label{fig:android-app-1}
	}
	\hfil
	\subfloat[Autostart OSGi Framework]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-2}
		\label{fig:android-app-2}}
	\hfil
	\subfloat[Bundle Page]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-app-3}
		\label{fig:android-app-3}}
	\caption{Android Application}
	\label{fig:android-app}
\end{figure}

@@

\subsubsection{Proxy Server}
Proxy server is an OSGi bundle that implements an embedded web server. Web server used in this study is Jetty 9 which is the highest major version available today. In the Proxy Server Bundle registered a service (API) ContextHandlerService, which is used to register the ServletContext initiated on Application Bundle.

\subsubsection{Composite Application}
Composite Application is an OSGi bundle that implements web services and clients in a same bundle. Web services are implemented in the form of Servlets collected in a single context. While the client is implemented in the form of a web-based application, written in HTML, Javascript, and CSS. In addition, the Composite Application also provides an API that can be imported dynamically by another bundle, ie: AccountHandlerService, DaoHandlerService, and PropertyHandlerService.

\subsubsection{Synchronizer}
Synchronizer is an OSGi bundle that is used to synchronize data in two directions: Remote to Local and Local to Remote. Synchronizer bundle requires some service provided by Composite Application, ie: AccountHandlerService to access the session to be synchronized and DaoHandlerService to access local storage.

\figurename{\ref{fig:android-bundle}} shows screenshots of OSGi bundles installed and started in Android environment.

\begin{figure}
	\centering
	\subfloat[Install bundle]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-1}
		\label{fig:android-bundle-1}}
	\hfil
	\subfloat[Bundle is installing]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-2}
		\label{fig:android-bundle-2}}
	\hfil
	\subfloat[Bundles are installed]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-3}
		\label{fig:android-bundle-3}}
	\vfil
	\subfloat[Bundle is starting]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-4}
		\label{fig:android-bundle-4}}
	\hfil
	\subfloat[Bundles are active]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-5}
		\label{fig:android-bundle-5}}
	\hfil
	\subfloat[Composite application is loaded]{
		\centering
		\includegraphics[width=2.5cm]{../Images/android-bundle-6}
		\label{fig:android-bundle-6}}
	\caption{Android Bundles}
	\label{fig:android-bundle}
\end{figure}

\subsection{Remote Server}
As described in \ref{ssec:android-application}, Knopflerfish by default already provides an implementation of the OSGi Framework that can be run on any operating system that supports Java SE. Remote server running Knopflerfish using minimal bundle, and installed the same module with the composite application. Listing.\ref{lst:start-framework-remote} and Listing.\ref{lst:start-bundle-remote} shows screenshots of OSGi bundles are active in remote server.

\begin{listing}
    \caption{Knopflerfish with minimal bundles}
    \begin{minted}[showspaces=false,breaklines=true]{java}
java -jar framework.jar -xargs minimal.xargs
Knopflerfish OSGi framework launcher, version <unknown>
Copyright 2003-2015 Knopflerfish. All Rights Reserved.
See http://www.knopflerfish.org for more information.

Created Framework: org.knopflerfish.framework, version=7.2.0.
> Framework launched
	\end{minted}
    \label{lst:start-framework-remote}
\end{listing}

\begin{listing}
    \caption{Install and start required bundles}
    \begin{minted}[showspaces=false,breaklines=true]{java}
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/proxy-server-9.0.7.v20131107-dex.jar
Installed: Proxy Server (#10)
> start 10
2016-09-05 21:57:02.294:INFO:oejs.Server:BundleStart #10: jetty-9.0.z-SNAPSHOT
2016-09-05 21:57:02.455:INFO:oejs.ServerConnector:BundleStart #10: Started ServerConnector@698b6705{HTTP/1.1}{0.0.0.0:5555}
Started: Proxy Server (#10)
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/se2016-bundle-0.1-SNAPSHOT-dex.jar
Installed: SE2016 - Application (#11)
> start 11
...
2016-09-05 21:57:33.147:INFO:oejsh.ContextHandler:BundleStart #11: Started o.e.j.s.ServletContextHandler@390161c7{/se2016,null,AVAILABLE}
Started: SE2016 - Application (#11)
> install http://knopflerfish.soedomoto.tk/jars/pgfw7/se2016-sync-bundle-0.1-SNAPSHOT-dex.jar
Installed: SE2016 - Sync Module (#12)
> start 12
Started: SE2016 - Sync Module (#12)
...
	\end{minted}
    \label{lst:start-bundle-remote}
\end{listing}

@@

\section{Conclusion and Future Work}
We propose a mobile proxy design that is dynamic, which can be distributed separately with composite applications and its synchronization. Distribution of proxy server, composite applications, and synchronization is done in the form of OSGi bundle. By adopting the principles of OSGi, synchronization workflows in the form of web services proved to be more effective, because each bundle can be updated independently, either manually or automatically.

By adopting the synchronization in a separate module also proven to be able to synchronize with better and more controlled because it can be start-stop and in every moment. Synchronization modules can also be updated, either manually or automatically, without affecting the other modules.

Our proposed design also makes it possible to install more than one composite applications and synchronization in an application with just a single proxy server.

@@

% use section* for acknowledgment
% \section*{Acknowledgment}
% The authors would like to thank...
